%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }

    \newenvironment{projectlong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Abdelrahman Khaled} \\[7.5pt]
\href{https://github.com/AKhalid-projects}{\raisebox{-0.05\height}\faGithub\ AKhalid-projects} \ $|$ \ 
\href{https://www.linkedin.com/in/abdelrahman-khalid/}{\raisebox{-0.05\height}\faLinkedin\ Abdelrahman Khalid} \ $|$ \ 
\href{mailto:abdulrahmankhalid797@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ abdulrahmankhalid797@gmail.com} \\
\href{tel:+97337320462}{\raisebox{-0.05\height}\faMobile \ +973 3732 0462} \ $|$ \ 
\href{https://www.credly.com/users/abdelrahman-khaled.ed6faa5e/badges}{\raisebox{-0.05\height}\faGlobe \ Credly} \  \ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{}
\begin{joblong}{Key Skills}{}
\item Cloud Platforms: AWS (EC2, S3, RDS), Azure, Google Cloud (GCP)
\item Cloud Architecture (DevOps): Kubernetes, Docker, Terraform, CI/CD (Jenkins, ArgoCD)
\item Programming Languages: JavaScript, Python, Node.js, React.js, Flutter
\item Backend Frameworks: Django, Laravel, Express.js
\item AI/ML Integration: AWS SageMaker, Google Cloud AI/ML
\item Cybersecurity: Vulnerability Assessments, Data Encryption, Secure Cloud Architectures
\item Automating Infrastructure: Serverless Architectures, Infrastructure as Code (IaC), Monitoring (Prometheus, Grafana)
\item Database Management: MongoDB, MySQL, PostgreSQL
\end{joblong}

%Experience
\section{Work Experience}

\begin{joblong}{Co-Founder (CTO) | Venustusy}{Feb 2022 - present}
\item Cloud Architecture and Infrastructure: Designed and implemented scalable cloud architectures on AWS, Azure, and GCP for diverse clients, focusing on high availability, cost optimization, and security best practices. 
\item Led multiple cloud migration and infrastructure automation projects, utilizing Kubernetes, Docker, and Terraform.
\item Full-Stack Software Development: Led development teams in delivering full-stack web and mobile applications using modern frameworks and technologies like React.js, Node.js, Django, and Flutter. Ensured best practices in DevOps with automated CI/CD pipelines and container orchestration.
\item Cybersecurity and Compliance: Implemented comprehensive cybersecurity solutions, including encryption protocols, vulnerability assessments, and compliance audits to ensure secure application deployments and data protection.
\item AI/ML Integration: Delivered AI/ML solutions using Google Cloud and AWS SageMaker for business intelligence, process automation, and predictive analytics, optimizing client operations in industries like healthcare and finance.
\item Leadership and Project Delivery: Managed cross-functional engineering teams, driving the successful delivery of over 20 projects with a focus on technical excellence and client satisfaction. Collaborated directly with stakeholders to translate business requirements into technical solutions.
\end{joblong}


\begin{joblong}{AWS Authorized Instructor | Nasser Vocational Training Centre (NVTC)}{Aug 2022 - present}
\item Developed and delivered cloud computing, AI, and cybersecurity curricula aligned with AWS certification standards.
\item Led workshops, hackathons, and coding competitions to enhance learners' practical skills and prepare them for AWS certifications.
\item Established partnerships with key industry players to provide students with real-world exposure, networking opportunities, and pathways for internships or employment, bridging the gap between academic learning and professional experience.
\item Created courses in cloud computing, programming, and IoT, and mentored senior projects to support learners' career development.
\item Played a pivotal role in securing NVTC’s status as an AWS Authorized Training Partner, establishing the institution as a recognized center for AWS training and certification, which has significantly expanded the reach and impact of the cloud computing programs offered.

\end{joblong}

\begin{joblong}{Software Development Engineer I (SDE I) | Mannai Tech}{Jan 2022 - Aug 2022}
    \item Enhanced User Experience and Global Reach: Successfully implemented multi-language support and user interface improvements for the CODOT client application, significantly enhancing user accessibility and expanding the application's global reach.
    \item Secured Data and Streamlined Operations: Developed and implemented robust authentication and authorization protocols for the CarFlow application, ensuring secure data access and management. Additionally, I integrated and managed a Shopify e-commerce platform for Karima Sharabi, streamlining online sales operations and providing a seamless customer experience.
    \item Technical Proficiency: Demonstrated proficiency in ( JavaScript, Tailwind CSS, React.js, Vue.js, Laravel, Inertia.js, and Node.js ).
    
\end{joblong}

\begin{joblong}{Software Engineer Intern | Unipal}{Sep 2021 - Dec 2021}
    \item Cost-Efficient Serverless Architecture: Architected and prototyped a serverless architecture for the merchant dashboard, significantly reducing operational costs and improving scalability.
    \item Enhanced SEO Performance: Optimized Unipal's SEO through server-side rendering, leading to a 10 percent improvement in search engine ranking and increased organic traffic.
    \item Technical Expertise: Demonstrated proficiency in ( JavaScript, Node.js, React, Tailwind CSS, AWS, and APIs ).

\end{joblong}

\begin{joblong}{Google Cloud Champion Innovator - Cloud AI/ML}{Feb 2022 - Present}
\item Recognition and Expertise: Recognized by Google as a Cloud AI/ML Champion Innovator, joining a global network of leading cloud professionals. This distinction highlights my expertise and contributions to Google Cloud's AI and Machine Learning solutions.
\item Exclusive Access and Collaboration: Granted exclusive access to Google Cloud product teams and projects, fostering collaboration and early engagement with cutting-edge cloud technologies.
\item Community Leadership: Awarded recognized member status on the Stack Overflow Google Cloud Collective, a prestigious community of experts. Actively contribute to knowledge sharing, technical discussions, and mentorship within the Google Cloud domain.

\end{joblong}

\begin{joblong}{GDSC Mentor - MENA}{Jul 2021 - Feb 2022}
\item Mentorship and Empowerment: Provided technical mentorship and hands-on labs to over 1500 students across the MENA region, empowering them to pursue careers in data analytics.
\item Community Building and Collaboration: Co-hosted workshops and sessions with other GDSC chapters, reaching an additional 1000 participants and fostering collaboration within the tech community.
\item Recognition for Contributions: Recognized as a Google Cloud Champion Innovator in AI/ML for my contributions to the program and the broader Google Developer Communities ecosystem.

\end{joblong}

\begin{joblong}{GDSC Founder and Lead}{Sep 2019 - Sep 2021}
\item Chapter Establishment and Growth: Founded and led a thriving GDSC chapter at the University of Bahrain, promoting Google technologies and fostering student engagement in the tech ecosystem.
\item Community Impact: Organized and hosted over 150 technical workshops and sessions, impacting over 5000 learners.
\item Collaboration and Outreach: Co-organized events with external tech communities, attracting over 2000 participants and facilitating collaboration and knowledge exchange.

\end{joblong}
  
%LProjects
\section{Projects}

\begin{projectlong}{Multilingual Document Translation Application}{}
    \item Developed a full-stack document translation application using React.js for the frontend and a robust Python backend with AWS integration. This user-friendly application allows users to upload various document formats (text, PDF, PowerPoint, Excel), select source and target languages, and receive translated versions with preserved original formatting.
\end{projectlong}

\begin{projectlong}{Customizable Automation Platform}{}
    \item Designed and developed a highly scalable automation platform that enables users to connect various popular tools and automate tasks.
            Utilized Next.js, Tailwind CSS, and Prisma for a robust and efficient infrastructure.
            Implemented seamless integrations with Discord, Slack, Google Drive, and Notion.
            Created a user-friendly interface with a drag-and-drop node builder and visual workflow map.
            Developed a subscription-based pricing model using Stripe.
            Technologies: Next.js 14, ngrok, Tailwind CSS, Aceternity UI, Chadcn UI, Prisma, Neon tech, Uploadcare, Cron jobs, Zustand, Stripe, React Flow, Clerk authentication
\end{projectlong}

\begin{projectlong}{FocusPoint - Photography Portfolio Website}{}
    \item Designed and developed a dynamic, visually appealing portfolio website to showcase photography work.
Utilized React for a modern and interactive user experience.
Leveraged Netlify for seamless deployment and hosting.
Integrated MongoDB as a flexible and scalable database for storing and managing content.
Implemented a CMS for easy content management, allowing for effortless updates of photos and descriptions.
\end{projectlong}




%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2017 - 2022 & Software Engineering Bachelor's Degree at \textbf{University of Bahrain}  \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
%	Certifications
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2024 & \textbf{CKA: Certified Kubernetes Administrator}  \\ 
2024 & \textbf{Google Cloud Certified Professional Cloud Architect} \\
2024 & \textbf{AWS Certified Solutions Architect Associate}  \\
2024 & \textbf{Oracle Cloud Infrastructure 2024 DevOps Professional (1Z0-1109-24)} \\
2024 & \textbf{KCNA: Kubernetes and Cloud Native Associate}  \\ 
2023 & \textbf{AWS Verified Educator}  \\ 
2023 & \textbf{Google Cloud Champion Innovator - Cloud AI/ML}  \\ 
2022 & \textbf{Certified Microsoft Azure Administrator Associate}  \\ 
\end{tabularx}


%------------------------------------------------------------------------------- ---------
%	Volunteering & Contributions
%----------------------------------------------------------------------------------------
\section{Volunteering and Contributions}


\textbf{Community Engagement and Knowledge Sharing} \\
\\
\begin{tabularx}{\linewidth}{@{}l X@{}}	
Focus Group Member & \textbf{Participated in the Focus Group for Packt's AWS Solutions Architect Associate (SAA-C02) Practice Exams, contributing valuable insights and feedback to developing exam preparation resources.}  \\
\\
E-book Translator & \textbf{Translated the e-book "Terraform Best Practices" into Arabic, expanding access to essential knowledge and skills within the Arabic-speaking community.}  \\ 
\\
Technical Content Contributor & \textbf{Contributed to the "Introduction to DevOps on AWS Whitepaper," sharing technical expertise and supporting disseminating valuable information.}  \\ 
\\
\\
\end{tabularx}


\end{document}
    
